
\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{tabularx}


\begin{document}
%
\title{Data Mining 1: \\
Predicting positions of soccer players  \\
Project Report}
\authorrunning{Data Mining 1 Team 9}

\vspace{2cm}
\author{Team No. 9\\
\vspace{1cm}
presented by\\
Jurgen Amedani (1628022), Cara Maria Damm (1631263), Paul Hesselmann (1371380), Allwyn Menezes (1671634), Martin Mlinac (1364487), Carmen Rannefeld (1631070)\\
\vspace{1cm}
submitted to the \\
Data and Web Science Group\\
Prof. Dr. Bizer\\
University of Mannheim}

\institute{}
\maketitle              % typeset the header of the contribution
\newpage
%1. What is the problem you are solving?
\input{intro.tex}
\input{data.tex}
\input{pre.tex}
\input{datamining.tex}
\newpage









% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%

\bibliographystyle{splncs04}
\bibliography{mybibliography}
%
\begin{thebibliography}{8}

\bibitem{ref_Transfermarkt}
Die Transfermarkt Top Marktwerte, URL: \url{https://www.transfermarkt.de/1-bundesliga/marktwerte/wettbewerb/L1}. Last accessed May, 17 2019

\bibitem{ref_Crowdflower}
Crowdflower 2016 data science report, 2016   URL: \url{https://visit.figure-eight.com/data-science-report.html}. Last accessed May, 17 2019

\bibitem{ref_sofifa}
Sofifa.com \url{https://sofifa.com/players}. Last accessed May, 12 2019

\bibitem{ref_rapidminergbt}
Rapidminer Documentation GBT, URL: \url{https://docs.rapidminer.com/latest/studio/\newline operators/modeling/predictive/trees/gradient\_boosted\_trees.html}, last accessed May 12, 2019


\bibitem{ref_towardsGBT}
Towards Data Science: Understanding Gradient Boosting Machines, URL:  \url{https://towardsdatascience.com/understanding-gradient-boosting-machines-9be756fe76ab}. Last accessed May 22, 2019
%\bibitem{ref_gitplayerstatistics}
%Sofifa.com \url{https://github.com/amanthedorkknight/fifa18-all-player-statistics/blob/master/README.md}. Last accessed May, 12 2019

\bibitem{ref_rapidminersvm}
Rapidminer Documentation SVM, URL: \url{https://docs.rapidminer.com/8.2/studio/\newline operators/modeling/predictive/support\_vector\_machines/support\_vector\_machine.html}. Last accessed May 22, 2019

\bibitem{ref_rapidminersvm2}
Rapidminer Documentation SVM Evolutionary, URL: \url{https://docs.rapidminer.com/latest/studio/operators/modeling/predictive/\newline support\_vector\_machines/support\_vector\_machine\_evolutionary.html}. Last accessed May 22, 2019

\bibitem{ref_rapidminerRandomForest}
Rapidminer Documentation Random Forest, URL: \url{https://docs.rapidminer.com/latest/studio/operators/\newline modeling/predictive/trees/parallel\_random\_forest.html}. Last accessed May 22,2019

\bibitem{ref_Tan}
Tan, Pang-Ning, Michael Steinbach, and Vipin Kumar. Introduction to Data Mining. Pearson International ed. Boston Munich [u.a., 2006. Print. Pearson International Edition.]

\bibitem{ref_svm}
Rapid Miner Support Vector Machines, URL: \url{https://docs.rapidminer.com/8.2/studio/operators/modeling/predictive\newline/support\_vector\_machines/support\_vector\_machine.html}. Last accessed May 20, 2019
%
\bibitem{ref_svm2}
Rapid Miner Support Vector Machines Evolution, URL: \url{https://docs.rapidminer.com/latest/studio/operators/modeling/predictive\newline/support\_vector\_machines/support\_vector\_machine\_evolutionary.html}. Last accessed May 20, 2019





\end{thebibliography}
\end{document}
